---
title: "Analyze Associations between Sleep and Caregiving"
output: html_notebook
---

##Load data
```{r load_data}
##Libraries
library(tidyverse)
library(lme4)
library(lmerTest)
library(jtools)
library(nlme)
library(corrr)
library(sjstats)
library(psych)

##Parameters

#files_________________________________________________________________
intervention_file <- "~/Desktop/BABIES/manber_sleep/data/ID and Tx Arm.csv"

demographics_file <- "~/Desktop/BABIES/manber_sleep/data/Demographics_02.15.18.xlsx"

infant_age_file <- "~/Desktop/BABIES/manber_sleep/data/ID and Delivery_Day.xlsx"
```

# Read in data: wide format
```{r}
data_wf <-
  free_play_wf %>% 
  left_join(
    read_csv(intervention_file) %>% 
      mutate(
        ID = as.numeric(ID),
        Condition = if_else(
          Condition == "ABTi",
          "ABTI", Condition
        )
      ),
    by = "ID"
  ) %>%  
  left_join(questionnaires, by = "ID") %>% 
  left_join(actigraphy_wf, by = "ID") %>% 
  left_join(
    readxl::read_xlsx(demographics_file, sheet = "Demographics_02.15.18") %>% 
      select(
        ID,
        site = SITE,
        mom_dob = DOB,
        latino = Eth_latino,
        race = Race,
        education = Education,
        income = Income
      ),
    by = "ID"
  ) %>% 
  left_join(sleep_diary_wf, by = "ID")  %>% 
  left_join(
    readxl::read_xlsx(
      infant_age_file, 
      sheet = "Sheet1"
      ),
    by = "ID"
  ) %>% 
  mutate(
    mom_age = (mom_dob %--% date_fp) / years(1),
    baby_age = (Delivery_Day %--% date_fp) / months(1)
  ) %>% 
  select(-Delivery_Day, -mom_dob)


```

# Read in data: long format
```{r}
data_lf <-
  free_play_lf %>% 
  filter(Episode != 6) %>% 
  left_join(
    read_csv(intervention_file) %>% 
      mutate(
        ID = as.numeric(ID),
        Condition = if_else(
          Condition == "ABTi",
          "ABTI", Condition
        )
      ),
    by = "ID"
  ) %>% 
  left_join(questionnaires, by = "ID") %>% 
  left_join(actigraphy_wf, by = "ID") %>% 
  left_join(
    readxl::read_xlsx(demographics_file, sheet = "Demographics_02.15.18") %>% 
      select(
        ID,
        site = SITE,
        mom_dob = DOB,
        latino = Eth_latino,
        race = Race,
        education = Education,
        income = Income
      ),
    by = "ID"
  ) %>% 
  left_join(sleep_diary_wf, by = "ID") %>%
  mutate(
    episode_re = as.integer(
      recode(
        Episode,
        "1" = "0",
        "2" = "1",
        "3" = "2",
        "4" = "3",
        "5" = "4"
      )
    ),
    mom_age = (mom_dob %--% date_fp) / years(1)
  )

```

# Descriptives
## Ns
```{r}
data_wf %>% 
  count(!is.na(sens_M), !is.na(wake_time_ac)) %>% 
  mutate(
    per = n / sum(n)
  )

data_wf %>% 
  count(!is.na(sens_M), !is.na(wake_time_sd)) %>% 
  mutate(
    per = n / sum(n)
  )

data_wf %>% 
  count(!is.na(sens_M), !is.na(sleep_time_sd)) %>% 
  mutate(
    per = n / sum(n)
  )
  
data_wf %>% 
  count(!is.na(sens_M), !is.na(ISI_total)) %>% 
  mutate(
    per = n / sum(n)
  )

data_wf %>% 
  count(!is.na(sens_M), !is.na(EPDS_total)) %>% 
  mutate(
    per = n / sum(n)
  )

data_wf %>% 
  filter(!is.na(sens_M)) %>% 
  count(site)

semi_join(actigraphy_wf, sleep_diary_wf) %>% count()
```

## Demographics
```{r}
data_wf %>% 
  count(Condition)

##age
data_wf %>% 
  summarise_at(
    vars(mom_age, baby_age),
    funs(mean, sd, min, max), na.rm = TRUE
  )

data_wf %>% 
  group_by(Condition) %>% 
  summarise_at(
    vars(mom_age),
    funs(mean, sd), na.rm = TRUE
  )


##education
data_wf %>% 
  count(education) %>% 
  mutate(
    per = n / sum(n)
  )

data_wf %>% 
  group_by(Condition) %>% 
  count(education) %>% 
  mutate(
    per = n / sum(n)
  )

data_wf %>% 
  summarise(
    median(education) #7 = Graduate or professional degree
  )

##income
data_wf %>% 
  count(income) %>% 
  mutate(
    per = n / sum(n)
  )

data_wf %>% 
  group_by(Condition) %>% 
  count(income) %>% 
  mutate(
    per = n / sum(n)
  )

data_wf %>% 
  filter(income != "6") %>% 
  summarise(
    median(income) #5 = $100,000 or More 
  )

##ethnicity
data_wf %>% 
  count(latino) %>% 
  mutate(
    per = n / sum(n)
  )

data_wf %>% 
  group_by(Condition) %>% 
  count(latino) %>% 
  mutate(
    per = n / sum(n)
  )

#race
data_wf %>% 
  count(race) %>% 
  mutate(
    per = n / sum(n)
  )

data_wf %>% 
  group_by(Condition) %>% 
  count(race) %>% 
  mutate(
    per = n / sum(n)
  )
```

## Sleep and symptom measures

```{r}
#overall
data_wf %>% 
  summarise_at(
    vars(
      n_days_ac,
      n_days_sd,
      wake_time_ac, 
      wake_bouts_ac, 
      sleep_time_ac, 
      wake_time_sd,
      wake_bouts_sd,
      sleep_time_sd,
      quality_sd,
      ISI_total, 
      EPDS_total
      ),
    funs(mean, sd, min, max), na.rm = TRUE
  )

#by intervention condition
data_wf %>% 
  group_by(Condition) %>% 
  summarise_at(
    vars(
      n_days_ac,
      n_days_sd,
      wake_time_ac, 
      wake_bouts_ac, 
      sleep_time_ac, 
      wake_time_sd,
      wake_bouts_sd,
      sleep_time_sd,
      quality_sd,
      ISI_total, 
      EPDS_total
      ),
    funs(mean, sd, min, max), na.rm = TRUE
  )
```

```{r}
#number of days of actigraphy
data_wf %>% 
  count(n_days_ac) %>% 
  arrange(desc(n_days_ac))

corr_sd_days <- 
  data_wf %>%
  select(
    n_days_sd,
    wake_time_sd,
    wake_bouts_sd,
    sleep_time_sd,
    quality_sd
  ) %>% 
  correlate(use = "complete.obs", method = "pearson") %>% 
  fashion()
corr_sd_days

corr_ac_days <- 
  data_wf %>%
  select(
    n_days_ac,
    wake_time_ac,
    wake_bouts_ac,
    sleep_time_ac
  ) %>% 
  correlate(use = "complete.obs", method = "pearson") %>% 
  fashion()
corr_ac_days
```

# Create income variable removing "Don't know" responses
```{r}
data_wf <- 
  data_wf %>% 
  mutate(
    income_clean = if_else(income == 6, NA_real_, income)
  )

data_lf <- 
  data_lf %>% 
  mutate(
    income_clean = if_else(income == 6, NA_real_, income)
  )
```

## Dimensionality Reduction

### Correlations among sleep measures
```{r}
corr_sleep_matrix <- 
  data_wf %>%
  select(
    wake_time_ac,
    wake_bouts_ac,
    sleep_time_ac,
    wake_time_sd,
    wake_bouts_sd,
    sleep_time_sd,
    quality_sd
  ) %>% 
  correlate(use = "complete.obs", method = "pearson") %>% 
  fashion()
corr_sleep_matrix <- corr_sleep_matrix
```

```{r}
corr_sleep_plot <- 
  data_wf %>%
  select(
    `Objective WASO` = wake_time_ac,
    `Objective arousals` = wake_bouts_ac,
    `Objective TST` = sleep_time_ac,
    `Subjective WASO` = wake_time_sd,
    `Subjective awakenings` = wake_bouts_sd,
    `Subjective TST` = sleep_time_sd,
    `Perceived quality` = quality_sd
  ) %>% 
  cor(use = "complete.obs", method = "pearson")

ggcorrplot(corr_sleep_plot)
```

```{r}
#actigraphy with actigraphy
cor.test(data_wf$wake_time_ac, data_wf$wake_bouts_ac)
cor.test(data_wf$wake_time_ac, data_wf$sleep_time_ac)
cor.test(data_wf$wake_bouts_ac, data_wf$sleep_time_ac)

#subjective with subjective
cor.test(data_wf$wake_time_sd, data_wf$wake_bouts_sd)
cor.test(data_wf$wake_time_sd, data_wf$sleep_time_sd)
cor.test(data_wf$wake_time_sd, data_wf$quality_sd)

#actigraphy with subjective
cor.test(data_wf$wake_time_ac, data_wf$wake_time_sd)
cor.test(data_wf$wake_bouts_ac, data_wf$wake_bouts_sd)
cor.test(data_wf$sleep_time_ac, data_wf$sleep_time_sd)
cor.test(data_wf$sleep_time_ac, data_wf$wake_time_sd)
cor.test(data_wf$sleep_time_ac, data_wf$wake_bouts_sd)
cor.test(data_wf$sleep_time_ac, data_wf$quality_sd)
```

### EFA of sleep measures

```{r}
data_sleep_efa <-
  data_wf %>% 
  dplyr::select(
    wake_time_ac,
    wake_bouts_ac,
    sleep_time_ac,
    wake_time_sd,
    wake_bouts_sd,
    sleep_time_sd,
    quality_sd
  )

```

#### Check factorability
Barlett's test: Compare correlation matrix to identify matrix (no correlation matrix). Null is that there is no difference between the matrices. 
```{r}
cortest.bartlett(corr_sleep_plot)
```

```{r}
VSS.scree(data_sleep_efa)
```

I will use the minimum residual method to extract the factors. This is the default method in fa() and minimizes the residual matrix (the difference between the original correlation matrix and the matrix of the extracted factors). I will use varimax rotation to impose orthogonality of the factors and improve intepretability. I am imputing missing values with the mean. 

#### 2-factor EFA
```{r}
EFA_sleep_2 <-
  fa(
  data_sleep_efa, 
  nfactors = 2,
  cor = "cor",
  rotate = "varimax",
  missing = TRUE,
  impute = "mean",
  fm = "minres"
)

EFA_sleep_2
EFA_sleep_2$loadings

EFA_sleep_2$Vaccounted[3,2]
```

Dropping sleep_time_ac because of weak loadings.
```{r}
data_sleep_efa_final <-
  data_wf %>% 
  dplyr::select(
    wake_time_ac,
    wake_bouts_ac,
    wake_time_sd,
    wake_bouts_sd,
    sleep_time_sd,
    quality_sd
  )
```

```{r}
EFA_sleep_2_final <-
  fa(
  data_sleep_efa_final, 
  nfactors = 2,
  cor = "cor",
  rotate = "varimax",
  missing = TRUE,
  impute = "mean",
  fm = "minres"
)

EFA_sleep_2_final
EFA_sleep_2_final$loadings

EFA_sleep_2_final$Vaccounted[3,2]
```

Collectively explain 59% of the variance. 

F1 = sleep_time_sd and quality_sd, -wake_time_sd, -wake_bouts_sd
F2 = wake_time_ac, wake_bouts_ac

#### Heatmap of 2-factor solution

```{r}
factor_names = c(
  "Factor 1:\nSubjective sleep disturbance", 
  "Factor 2:\nObjective sleep continuity"
  )

loadings <-
  EFA_sleep_2$loadings[] %>% 
  data.frame() %>% 
  rownames_to_column("measure") %>% 
  gather(factor, loading, -measure) %>%  
  mutate(factor = as.character(factor(factor, labels = factor_names))) 
  

# get fa.sort() order
order <- 
  loadings %>%
  group_by(measure) %>%
  top_n(1, abs(loading)) %>%
  ungroup() %>%
  arrange(desc(factor), abs(loading)) %>%
  mutate(order = 1:length(levels(factor(loadings$measure)))) %>%
  select(measure, order)
  
# get percent shared variance explained
shared_var <- EFA_sleep_2$Vaccounted %>%
  data.frame() %>%
  rownames_to_column("stat") %>%
  filter(stat == "Proportion Var") %>%
  select(-stat) %>%
  gather(factor, var) %>%
  mutate(factor = as.character(factor(factor, labels = factor_names))) %>%
  mutate(var = paste0(factor, "\n(", round(var, 2)*100, "% var.)"))

  # make plot
loadings_plot_data <- 
  loadings %>% 
  left_join(order, by = "measure") %>%
  left_join(shared_var, by = "factor") %>%
  mutate(
    measure = recode(
    measure,
    "sleep_time_sd" = "Subjective TST",
    "wake_time_sd" = "Subjective WASO",
    "quality_sd" = "Perceived quality",
    "wake_bouts_sd" = "Subjective awakenings",
    "wake_time_ac" = "Objective WASO",
    "wake_bouts_ac" = "Objective arousals"
    )
  ) 

loadings_plot_data %>% 
  ggplot(
    aes(
      x = var, 
      y = reorder(measure, order), 
      fill = loading,
      label = round(loading, 2)
    )
  ) +
  geom_tile(color = "black") +
  geom_text(size = 7, color = "black") +
  scale_fill_distiller(
    limits = c(-1, 1), 
    palette = "RdYlBu",
    guide = guide_colorbar(barheight = 20)
  ) +
  scale_x_discrete(position = "top") +
  theme_minimal() +
  theme(
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    axis.title = element_blank(), 
    axis.text.y = element_text(size = 18),
    axis.text.x = element_text(size = 17)
  )

ggsave("~/Desktop/BABIES/manber_sleep/loadings_plot.png", height = 7, width = 10.5)
```

#### Compute sum scores for each factor
```{r}
data_wf <-
  data_wf %>% 
  mutate(
    sleep_disturbed_sd = scale(
      ((scale(wake_time_sd, scale = TRUE) + scale(wake_bouts_sd, scale = TRUE)) -
         (scale(sleep_time_sd, scale = TRUE) + scale(quality_sd, scale = TRUE))),
      scale = TRUE
    ), sleep_continuity_ac = scale(
      (scale(wake_time_ac, scale = TRUE) + scale(wake_bouts_ac, scale = TRUE)),
      scale = TRUE
    ) * -1
  )

data_wf %>% 
  ggplot(aes(sleep_disturbed_sd)) +
  geom_histogram()

data_wf %>% 
  ggplot(aes(sleep_continuity_ac)) +
  geom_histogram()

```

## Trajectories of caregiving across the Free Play

##Recode variable for modeling
```{r}
data_lf <-
  data_lf %>% 
  left_join(
    data_wf %>% 
      select(ID, sleep_continuity_ac, sleep_disturbed_sd),
    by = "ID"
  ) %>% 
  mutate(
    Condition = as.factor(Condition),
    site = as.factor(site),
    episode_re_cent = scale(episode_re, scale = FALSE),
    wake_time_ac_cent = scale(wake_time_ac, scale = FALSE),
    isi_cent = scale(ISI_total, scale = FALSE),
    sleep_time_ac_cent = scale(sleep_time_ac, scale = FALSE),
    continuity_ac_hi = sleep_continuity_ac - sd(sleep_continuity_ac, na.rm = TRUE),
    continuity_ac_lo = sleep_continuity_ac + sd(sleep_continuity_ac, na.rm = TRUE),
    negmood_cent = scale(negmood_fin, scale = FALSE),
    epds_cent = scale(EPDS_total, scale = FALSE),
    mom_age_cent = scale(mom_age, scale = FALSE),
    income_grp = as.factor(
      case_when(
        income == 6 ~ NA_character_,
        income < 5 ~ "lower",
        income == 5 ~ "higher"
      )
    ),
    site = case_when(
      site == "CR" ~ -.5,
      site == "SH" ~ 0,
      site == "VM" ~ .5
    )
  )

contrasts(data_lf$Condition) = c(-1, 1)
contrasts(data_lf$income_grp) = c(-1, 1)
```

##Primary analyses
```{r}
ml_base <- lmer(
  sens_fin ~ 
    episode_re + 
    Condition + 
    site + 
    (1|ID), 
  REML = FALSE,
  data = data_lf
  )

summary(ml_base)
```

### subjective sleep disturbance
```{r}
ml_SD <- lmer(
  sens_fin ~ 
    episode_re * sleep_disturbed_sd + 
    Condition + 
    site + 
    (1|ID), 
  REML = FALSE,
  data = data_lf
  )

summary(ml_SD)
std_beta(ml_SD)
```

### objective sleep continuity
```{r}
ml_SC <- lmer(
  sens_fin ~ 
    episode_re * sleep_continuity_ac + 
    Condition + 
    site + 
    (1|ID), 
  REML = FALSE,
  data = data_lf
  )

summary(ml_SC)
std_beta(ml_SC)
```

#### objective sleep contunuity: simple slopes
```{r}
ml_SC_lo <- lmer(
  sens_fin ~ 
    episode_re * continuity_ac_lo + 
    Condition + 
    site + 
    (1|ID), 
  REML = FALSE,
  data = data_lf
  )

summary(ml_SC_lo)
std_beta(ml_SC_lo)
```

```{r}
ml_SC_hi <- lmer(
  sens_fin ~ 
    episode_re * continuity_ac_hi + 
    Condition + 
    site + 
    (1|ID), 
  REML = FALSE,
  data = data_lf
  )

summary(ml_SC_hi)
std_beta(ml_SC_hi)
```

#### objective sleep continuity: visualize

```{r}
##Extract intercepts and sloepes from models 
ml_SC_summary <- summary(ml_SC)
ml_SC_intercept <- ml_SC_summary$coefficients[1]
ml_SC_slope <- ml_SC_summary$coefficients[2]

ml_SC_lo_summary <- summary(ml_SC_lo)
ml_SC_lo_intercept <- ml_SC_lo_summary$coefficients[1]
ml_SC_lo_slope <- ml_SC_lo_summary$coefficients[2]

ml_SC_hi_summary <- summary(ml_SC_hi)
ml_SC_hi_intercept <- ml_SC_hi_summary$coefficients[1]
ml_SC_hi_slope <- ml_SC_hi_summary$coefficients[2]

simple_slopes_SC <- 
  tribble(
    ~effect, ~intercept, ~slope,
    "X Lower", ml_SC_lo_intercept, ml_SC_lo_slope,
    "Y Medium", ml_SC_intercept, ml_SC_slope,
    "Z Higher", ml_SC_hi_intercept, ml_SC_hi_slope
  )
```

```{r}
data_lf %>%   
  ggplot(aes(episode_re, sens_fin)) +
  geom_jitter(alpha = 1/11, size = .0001) + 
  theme(
    legend.position = "none"
  ) +
  geom_abline(
    data = simple_slopes_SC,
    aes(intercept = intercept, slope = slope, color = fct_rev(effect)),
    size = 5
  ) +
  scale_x_continuous(
    breaks = c(0, 1, 2, 3, 4),
    labels = c(2, 4, 6, 8, 10)
  ) +
  scale_y_continuous(
    breaks = seq.int(1, 6, 1)
  ) +
  scale_color_manual(
    labels = c("+1SD (better)", "Mean", "-1SD (poorer)"),
    values = c("indianred1", "darkgrey", " darkslategray1")
  ) +
  theme_minimal() +
  theme(
    #legend.position = "bottom",
    legend.text = element_text(size = 30),
    legend.title = element_text(size = 32),
    axis.title = element_text(size = 32),
    axis.text = element_text(size = 22),
    legend.key.size = unit(3, 'lines')
  ) +
  labs(
    color = "Objective\nsleep continuity",
    x = "Free play interval (minutes)",
    y = "Maternal sensitivity"
  )

ggsave("~/Desktop/BABIES/manber_sleep/manber_sleep_sync/plots/sens_continuity.png", width = 12, height = 10)


```

```{r}
cor.test(data_wf$`1_sens_fin`, data_wf$sleep_continuity_ac)
cor.test(data_wf$`2_sens_fin`, data_wf$sleep_continuity_ac)
cor.test(data_wf$`3_sens_fin`, data_wf$sleep_continuity_ac)
cor.test(data_wf$`4_sens_fin`, data_wf$sleep_continuity_ac)
cor.test(data_wf$`5_sens_fin`, data_wf$sleep_continuity_ac)


data_lf %>% 
  mutate(
    episode_factor = factor(
      episode_re,
      levels = c(0, 1, 2, 3, 4),
      labels = c(
        "0-2",
        "2-4",
        "4-6", 
        "6-8",
        "8-10"
      )
    )
  ) %>% 
  ggplot(aes(sleep_continuity_ac, sens_fin, color = episode_factor)) +
  geom_jitter(
    size = 6,
    alpha = 1/2
  ) +
  geom_smooth(
    method = "lm", 
    se = FALSE,
    size = 5,
    alpha = 1/2
  ) +
  scale_x_continuous(
    breaks = seq.int(-3, 3, .5)
  ) +
  scale_y_continuous(
    breaks = seq.int(0, 6, 1)
  ) +
  scale_colour_viridis_d() +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 30),
    legend.text = element_text(size = 28),
    axis.title = element_text(size = 30),
    axis.text = element_text(size = 22)
  ) +
  labs(
    color  = "Free play interval (minutes)",
    x = "Objective sleep continuity",
    y = "Maternal sensitivity"
  )
ggsave("~/Desktop/BABIES/manber_sleep/manber_sleep_sync/plots/sens_continuity_factor.png", width = 12, height = 10)
```

### Johnson-neyman wake time
```{r}
ml_WT <- lmer(
  sens_fin ~ 
    episode_re * wake_time_ac + 
    Condition + 
    site + 
    (1|ID), 
  REML = FALSE,
  data = data_lf
  )


johnson_neyman(ml_WT, pred = episode_re, modx = wake_time_ac, control.fdr = TRUE)
ggsave("~/Desktop/BABIES/manber_sleep/manber_sleep_sync/plots/johnson_neyman_wt.jpeg", width = 9, height = 7)

data_wf %>% 
  mutate(WT_group = wake_time_ac >= 52) %>% 
  filter(!is.na(WT_group)) %>% 
  count(WT_group) %>% 
  mutate(per = n / sum(n))
  
```

### Johnson-neyman wake bouts
```{r}
ml_WB <- lmer(
  sens_fin ~ 
    episode_re * wake_bouts_ac + 
    Condition + 
    site + 
    (1|ID), 
  REML = FALSE,
  data = data_lf
  )


johnson_neyman(ml_WB, pred = episode_re, modx = wake_bouts_ac, control.fdr = TRUE)
ggsave("~/Desktop/BABIES/manber_sleep/manber_sleep_sync/plots/johnson_neyman_wb.jpeg", width = 9, height = 7)

data_wf %>% 
  mutate(WB_group = wake_bouts_ac >= 17) %>% 
  filter(!is.na(WB_group)) %>% 
  count(WB_group) %>% 
  mutate(per = n / sum(n))
  
```



##Additional analyses

###adjusting for depression symptoms and infant negative mood
```{r}
ml_SC_cov <- lmer(
  sens_fin ~ 
    episode_re * sleep_continuity_ac + 
    Condition + 
    site + 
    episode_re * epds_cent +
    episode_re * negmood_cent +
    (1|ID), 
  REML = FALSE,
  data = data_lf
  )

summary(ml_SC_cov)
#confint(ml_WT_cov)
std_beta(ml_SC_cov)
```

###insomnia severity
```{r}
ml_ISI <- lmer(
  sens_fin ~ 
    episode_re * isi_cent + 
    Condition + 
    site + 
    (1|ID), 
  REML = FALSE,
  data = data_lf
  )

summary(ml_ISI)
std_beta(ml_ISI)

glimpse(data_lf)
```

##Evaluate differences between final sample and those who did not complete the free play

###Demographics
```{r}
demographics_all <- 
  readxl::read_xlsx(demographics_file, sheet = "Demographics_02.15.18") %>% 
  select(
    ID,
    site = SITE,
    mom_dob = DOB,
    latino = Eth_latino,
    race = Race,
    education = Education,
    income = Income
  ) %>% 
  left_join(
    free_play_wf %>% 
      select(
        ID,
        sens_M
      ),
    by = "ID"
  ) %>% 
  mutate(
    included = if_else(
      !is.na(sens_M),
      1, 0
    ),
    income_clean = if_else(income == 6, NA_real_, income)
  ) 

##site
demographics_all %>% 
  count(site, included) %>% 
  mutate(
    per = if_else(
      included == 1, 
      n / 67, n / 194
    )
  ) %>% 
  arrange(included)
    
##ethnicity
demographics_all %>% 
  count(latino, included) %>% 
  mutate(
    per = if_else(
      included == 1, 
      n / 67, n / 127
    )
  ) %>% 
  arrange(included)

##race
demographics_all %>% 
  mutate(
    white = if_else(
      race == 1,
      1, 0
    )
  ) %>% 
  count(white, included) %>% 
  mutate(
    per = if_else(
      included == 1, 
      n / 67, n / 127
    )
  ) %>% 
  arrange(included)


##race and eth
demographics_all %>% 
  mutate(
    white = if_else(
      race == 1,
      1, 0
    )
  ) %>% 
  count(white, latino, included) %>% 
  mutate(
    per = if_else(
      included == 1, 
      n / 67, n / 127
    )
  ) %>% 
  arrange(included)

##income
demographics_all %>% 
  filter(!is.na(income_clean)) %>% 
  mutate(
    income_grp = if_else(
      income_clean > 4, 
      "higher", "lower"
    )
  ) %>% 
  count(income_grp, included) %>% 
  mutate(
    per = if_else(
      included == 1, 
      n / 63, n / 115
    )
  ) %>% 
  arrange(included)

```

###ISI
```{r}
isi_all <- 
  questionnaires %>% 
  select(
    ID, 
    ISI_total
  ) %>% 
  left_join(
    free_play_wf %>% 
      select(
        ID,
        sens_M
      ),
    by = "ID"
  ) %>% 
  mutate(
    included = if_else(
      !is.na(sens_M),
      1, 0
    )
  )

isi_all %>% 
  filter(!is.na(ISI_total)) %>% 
  count(included)

isi_all %>% 
  group_by(included) %>% 
  summarise(
    mean(ISI_total, na.rm = TRUE)
  )

t.test(isi_all$ISI_total ~ isi_all$included)
```



