---
title: "Analyze Associations between Sleep and Caregiving"
output: html_notebook
---

##Load data
```{r load_data}
##Libraries
library(tidyverse)
library(lme4)
library(lmerTest)
library(jtools)
library(lcmm)

##Parameters
intervention_file <- "~/Desktop/BABIES/manber_sleep/ID and Tx Arm.csv"

plot_trajectories_id <- function(dataframe, x, y) {
  x_variable = enquo(x)
  y_variable = enquo(y)
  dataframe %>% 
  ggplot(aes(!! x_variable, !! y_variable)) +
    geom_jitter() +
    geom_smooth(
      aes(color = as.factor(ID)),
      method = "lm", 
      se = FALSE,
      alpha = 1/2
    ) +
    geom_smooth(
      method = "lm", 
      se = FALSE, 
      color = "black",
      size = 2
    ) +
    theme_minimal() +
    theme(
      legend.position = "none"
    )
}

plot_trajectories <- function(dataframe, x, y, color, method) {
  x_variable = enquo(x)
  y_variable = enquo(y)
  color_variable = enquo(color)
  
  dataframe %>% 
  ggplot(aes(x = !! x_variable, y = !! y_variable, color = !! color_variable)) +
    geom_jitter() +
    geom_smooth(
      method = method, 
      se = FALSE, 
      size = 2
    ) +
    theme_minimal() 
}
```

```{r}
data_wf <-
  free_play_wf %>% 
  left_join(free_play_fa %>% select(ID, Factor1:Factor3), by = "ID") %>%  
  left_join(read_csv(intervention_file), by = "ID") %>% 
  left_join(questionnaires, by = "ID") %>% 
  left_join(maternal_actigraphy_summary, by = "ID") 

data_lf <-
  free_play_lf %>% 
  filter(Episode != 6) %>% 
  left_join(read_csv(intervention_file), by = "ID") %>% 
  left_join(questionnaires, by = "ID") %>% 
  left_join(maternal_actigraphy_summary, by = "ID") %>% 
  mutate(
    episode_re = as.integer(
      recode(
        Episode,
        "1" = "0",
        "2" = "1",
        "3" = "2",
        "4" = "3",
        "5" = "4"
      )
    ),
    wake_time_grp = if_else(
      mean_wake_time > 60,
      "higher", "lower"
    ),
    efficiency_grp = if_else(
      mean_efficiency > median(mean_efficiency, na.rm = TRUE),
      "higher", "lower"
    ),
    ISI_grp = if_else(
      ISI_total > median(ISI_total, na.rm = TRUE),
      "higher", "lower"
    ),
    ISIP_grp = if_else(
      ISI_total > median(ISIP_total, na.rm = TRUE),
      "higher", "lower"
    )
  )
```

```{r}
corr_data_wf <- data_wf %>%
  select(
    ISI_total,
    ISIP_total,
    EPDS_total,
    mean_wake_time,
    mean_sleep_time,
    mean_efficiency,
    B_nightwakeful,
    B_sleepnight,
    B_gotosleep,
    B_sleepday,
    Factor1,
    Factor2,
    Factor3,
    sens_M,
    intrus_M
  )

corr_data_wf <- cor(corr_data_wf, use = "pairwise.complete.obs")
```

Actigraphy measure of maternal sleep time is not associated with either version of the ISI; however, measure of time awake is positively associated with both of these measures. 

##Trajectories of caregiving across the Free Play

###Plot trajectories

####sensitivity
```{r}
plot_trajectories_id(data_lf, episode_re, sens_fin)

##treatment arm
plot_trajectories_id(data_lf, episode_re, sens_fin) +
  facet_grid(~Condition)

plot_trajectories(data_lf, episode_re, sens_fin, Condition, method = "loess")

##wake time
plot_trajectories(
  data_lf %>% 
    filter(!is.na(wake_time_grp)),
  episode_re, 
  sens_fin, 
  wake_time_grp, 
  method = "loess"
) +
  theme(
    aspect.ratio = 1
  )

##efficiency
plot_trajectories(
  data_lf %>% 
    filter(!is.na(efficiency_grp)),
  episode_re, 
  sens_fin, 
  efficiency_grp, 
  method = "loess"
) +
  theme(
    aspect.ratio = 1
  )

```

####intrusiveness
```{r}
plot_trajectories_id(data_lf, episode_re, intrus_fin)

##treatment arm
plot_trajectories_id(data_lf, episode_re, intrus_fin) +
  facet_grid(~Condition)

plot_trajectories(data_lf, episode_re, intrus_fin, Condition, method = "loess")

##wake time
plot_trajectories(
  data_lf %>% 
    filter(!is.na(wake_time_grp)),
  episode_re, 
  intrus_fin, 
  wake_time_grp, 
  method = "loess"
) +
  theme(
    aspect.ratio = 1
  )

##efficiency
plot_trajectories(
  data_lf %>% 
    filter(!is.na(efficiency_grp)),
  episode_re, 
  intrus_fin, 
  efficiency_grp, 
  method = "loess"
) +
  theme(
    aspect.ratio = 1
  )
```

####stimulation
```{r}
plot_trajectories_id(data_lf, episode_re, stim_fin)

##treatment arm
plot_trajectories_id(data_lf, episode_re, stim_fin) +
  facet_grid(~Condition)

plot_trajectories(data_lf, episode_re, stim_fin, Condition, method = "loess")

##wake time
plot_trajectories(
  data_lf %>% 
    filter(!is.na(wake_time_grp)),
  episode_re, 
  stim_fin, 
  wake_time_grp, 
  method = "loess"
) +
  theme(
    aspect.ratio = 1
  )

##efficiency
plot_trajectories(
  data_lf %>% 
    filter(!is.na(efficiency_grp)),
  episode_re, 
  stim_fin, 
  efficiency_grp, 
  method = "loess"
) +
  theme(
    aspect.ratio = 1
  )

##insomnia severity
plot_trajectories(
  data_lf %>% 
    filter(!is.na(ISI_grp)),
  episode_re, 
  sens_fin, 
  ISI_grp, 
  method = "loess"
) +
  theme(
    aspect.ratio = 1
  )

##postpartum insomnia severity
plot_trajectories(
  data_lf %>% 
    filter(!is.na(ISIP_grp)),
  episode_re, 
  sens_fin, 
  ISIP_grp, 
  method = "loess"
) +
  theme(
    aspect.ratio = 1
  )

```

###Base Sensitivity MLM models
```{r}
sens_ml_1 <- lmer(sens_fin ~ Episode + (1|ID), REML = TRUE, data = data_lf)
summary(sens_ml_1)
sens_ml_2 <- lmer(sens_fin ~ Episode + (Episode|ID), REML = TRUE, data = data_lf)
summary(sens_ml_2)

ICC_intercept = .7612 / (.7612 + .3327)
ICC_intercept

ICC_slope = .03292 / (.74591 + .25163 + .03292)
ICC_slope
```
Slope ICC is very low. Will not include in models. 

###Sensitivity ~ Wake time MLM
```{r}
sens_ml_3 <- lmer(sens_fin ~ episode_re + mean_wake_time + (1|ID), REML = TRUE, data = data_lf)
summary(sens_ml_3)

sens_ml_4 <- lmer(sens_fin ~ episode_re * mean_wake_time + (1|ID), REML = TRUE, data = data_lf)

sens_ml_5 <- lmer(sens_fin ~ episode_re * scale(mean_wake_time, scale = FALSE) + (1|ID), REML = TRUE, data = data_lf)
summary(sens_ml_5)

johnson_neyman(model = sens_ml_4, pred = episode_re, modx = mean_wake_time)
```

###Intrusiveness ~ Wake time MLM
```{r}
intrus_ml_1 <- lmer(intrus_fin ~ episode_re + mean_wake_time + (1|ID), REML = TRUE, data = data_lf)
summary(intrus_ml_1)

sens_ml_5 <- lmer(intrus_fin ~ episode_re * scale(mean_wake_time, scale = FALSE) + (1|ID), REML = TRUE, data = data_lf)
summary(sens_ml_5)
```

###Intrusiveness ~ Wake time MLM
```{r}
stim_ml_1 <- lmer(stim_fin ~ episode_re + mean_wake_time + (1|ID), REML = TRUE, data = data_lf)
summary(stim_ml_1)

stim_ml_5 <- lmer(stim_fin ~ episode_re * scale(mean_wake_time, scale = FALSE) + (1|ID), REML = TRUE, data = data_lf)
summary(stim_ml_5)
```

###ISI MLM
```{r}
sens_ml_6 <- lmer(sens_fin ~ episode_re + ISI_total + (1|ID), REML = TRUE, data = data_lf)
summary(sens_ml_6)

sens_ml_7 <- lmer(sens_fin ~ episode_re * scale(ISI_total, scale = FALSE) + (1|ID), REML = TRUE, data = data_lf)
summary(sens_ml_7)
```

###ISI MLM
```{r}
sens_ml_8 <- lmer(sens_fin ~ episode_re + ISIP_total + (1|ID), REML = TRUE, data = data_lf)
summary(sens_ml_8)

sens_ml_9 <- lmer(sens_fin ~ episode_re * scale(ISIP_total, scale = FALSE) + (1|ID), REML = TRUE, data = data_lf)
summary(sens_ml_9)
```

##Means across intervention arms
```{r desc_cond}
data_wf %>% 
  group_by(Condition) %>%
  summarise_at(
    vars(
      ISI_total, 
      ISIP_total, 
      mean_wake_time,
      mean_efficiency,
      mean_sleep_time,
      sens_M:negreg_M
    ),
    funs(mean),
    na.rm = TRUE
  )
```
No substantial differences across actigraphy, self-report, or observational measures between though who received CBTI vs. ABTI. 

##Latent Class Mixture Model
```{r}
library(lcmm)

lcmm_sens_df <-
  data_lf %>% 
  select(
    ID,
    episode_re,
    sens_fin
  ) %>% 
  mutate(
    ID = as.character(ID)
  )

lcmm_sens <-
  lcmm(sens_fin~episode_re, random = ~episode_re, subject = "ID", mixture = ~episode_re, ng = 2, idiag = TRUE, data = lcmm_sens_df, link = "linear")

summary(lcmm_sens)
postprob(lcmm_sens)
```

```{r}
data_lf <-
  data_lf %>% 
  mutate(
    ID = as.character(ID)
  ) %>% 
  left_join(
    as.data.frame(lcmm_sens$pprob[, 1:3]) %>% 
      select(ID, class) %>% 
      mutate(
        class = as.character(class)
      ),
    by = "ID"
  ) 

plot_trajectories(data_lf, episode_re, sens_fin, class, method = "lm")

data_lf %>% 
  filter(!is.na(wake_time_grp)) %>% 
  ggplot(aes(class, sens_fin, fill = wake_time_grp)) +
  geom_col(position = "dodge")
```



NOTES:
DUKE
awakenings (amount of time awake) from mom and due to infant
early childhood adversity 
look at variability in sensitivity




